---
title: "Assignment 7"
output: word_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(randomForest)
library(caret)
library(gbm)
library(pROC)
library(rpart.plot)
library(rpart)
```

# Part 1


```{r}
set.seed(123)
hw7_data = read_csv("./mi.data.csv") %>% 
  janitor::clean_names()

#stripped id variable
hw7_data<-hw7_data[,2:16]

#changing variable types to appropriate ones
hw7_data$sex<-as.factor(hw7_data$sex)
hw7_data$pulm_adema<-as.factor(hw7_data$pulm_adema)
hw7_data$fc<-as.factor(hw7_data$fc)
hw7_data$arr<-as.factor(hw7_data$arr)
hw7_data$diab<-as.factor(hw7_data$diab)
hw7_data$obesity<-as.factor(hw7_data$obesity)
hw7_data$asthma<-as.factor(hw7_data$asthma)
hw7_data$readmission<-as.factor(hw7_data$readmission)

#re-leveling outcome variable: readmission (readmitted to hospital within 30 days) so "0=No" is reference group
hw7_data$readmission<-relevel(hw7_data$readmission, ref="0")

#omitting any missing data
hw7_data<-na.omit(hw7_data)
```

# Part 2 : Partition data into training and testing sets to 70/30 split

```{r}
set.seed(123)

training.data<-hw7_data$readmission %>% 
  createDataPartition(p=0.7, list=F)

#Training Data
train.data<-hw7_data[training.data, ]

#Testing Data
test.data<-hw7_data[-training.data, ]
```

# Comparing Two Different Algorithms: Elastic Net vs. Random Forest

Elastic Net Model
Model that chooses alpha and lambda via cross-validation using all of the features 
```{r, warning=FALSE}
set.seed(123)

train.control<-trainControl(method="cv", number=10, sampling="down")

elastic.model<- train(
  readmission ~., data = train.data, method = "glmnet",
  trControl = train.control, preProc=c("center", "scale"),
 tuneLength=10
  )

elastic.model$bestTune

confusionMatrix(elastic.model)
varImp(elastic.model)
plot(varImp(elastic.model))
```

Random Forest Model
Setting hyperparameters mtry (number of features eligible for each split)
```{r, warning=FALSE}
set.seed(123)

control.settings<-trainControl(method="cv", number=10, sampling="down")

#Producing various values of mtry
mtry.vals<-c(ncol(train.data)-1, sqrt(ncol(train.data)-1), 0.5*ncol(train.data)-1)
mtry.grid<-expand.grid(.mtry=round(mtry.vals))

rf_model<-train(readmission ~., data=train.data, method="rf", metric="Accuracy", tuneGrid=mtry.grid, trControl=control.settings, ntree=200)

confusionMatrix(rf_model)

varImp(rf_model)
plot(varImp(rf_model))
```

# Evaluation Metrics with Final Model - Elastic Model

```{r}
set.seed(123)

#Make predictions in test set
test.outcome<-predict(rf_model, newdata=test.data)

#Model Prediction Performance
confusionMatrix(test.outcome, test.data$readmission, positive="1")
```


